---
title: "Modern Information Workflows - Prework"
subtitle: "Becoming Proficient and Efficient with R and RStudio for Policy Work <html><div style='float:left'></div><hr color='#e2f1fc' size=1px width=1100px></html>"
author: 
- "<span style='color:#005f86; font-weight:500'>D. Cale Reeves</span> | Ph.D."
- "<span style='color:#005f86; font-weight:500'>Noorah Alhasan</span> | Ph.D."
- "<span style='color:#005f86; font-weight:500'>Matt Worthington</span> | M.Ed./M.PAff"
date: '<span style="color:#bf5700; font-weight:300">`r format(Sys.Date(), "%B %d, %Y")`</span>'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["xaringan-themer.css","assets/extra.css"]
    yolo: false
    nature:
      highlightStyle: github
      highlightLines: true
      beforeInit: "https://platform.twitter.com/widgets.js"
      countIncrementalSlides: false
      ratio: "16:9"
      navigation:
        scroll: false # disable slide transitions by scrolling
---
class: middle

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message = FALSE, warning = FALSE, comment = "", cache = FALSE, fig.retina = 3)
library(flipbookr)        # Makes Step-by-Step Code Demos
library(xaringanExtra)    # Package with Useful Stuff For Making Slides
library(tidyverse)        # What loads the core set of Modern R Packages, like ggplot2
library(tidycensus)       # Tidyverse-friendly connection to Census API
library(janitor)          # Really useful functions for cleaning data
library(lubridate)        # Makes Working With Dates Pretty Easy
library(grid)             # Organizes Visual Objects
library(ggtext)           # Helps with text in ggplot2 objects
library(cowplot)          # Helps with arranging and layering of ggplot2 objects 
library(hrbrthemes)       # A ppackage I really like with lots of useful functions
library(htmlwidgets)
library(lbjdata)
readRenviron("~/.Renviron")
census_api_key <- Sys.getenv("CENSUS_API_KEY")
```

```{r xaringanExtra, include=FALSE}
xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons", "webcam", "broadcast"))

xaringanExtra::use_share_again()
xaringanExtra::style_share_again(
  share_buttons = c("twitter", "linkedin")
)

xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         #<<
  mute_unhighlighted_code = TRUE  #<<
)

xaringanExtra::use_logo(
  image_url = "assets/lbj_white.svg"
)

xaringanExtra::use_fit_screen()

htmltools::tagList(
  xaringanExtra::use_clipboard(
    button_text = "<i class=\"fa fa-clipboard\"></i>",
    success_text = "<i class=\"fa fa-check\" style=\"color: #90BE6D\"></i>",
    error_text = "<i class=\"fa fa-times-circle\" style=\"color: #F94144\"></i>"
  ),
  rmarkdown::html_dependency_font_awesome()
)
```

# Prework

This is a resource to get prepared for the "Modern Information Workflows" workshop using R and Rstudio workshop that will be done on {INSERT DATE}. In order for the workshop to go smoothly and, more importantly, for you to get something out of it, you'll need to do a few things to get setup. If you have any questions during prework, please contact one of us at the following emails:

* D. Cale Reeves: [d.cale.reeves@utexas.edu](mailto:d.cale.reeves@utexas.edu)
* Noorah Alhasan: [noorah.alhasan@utexas.edu](mailto:noorah.alhasan@utexas.edu)
* Matt Worthington: [matthew.worthington@austin.utexas.edu](matthew.worthington@austin.utexas.edu)

---
class: middle

.pull-left[
## About The Workshop

In both professional work and in academic settings, projects are getting bigger, analyses are becoming more complex, and there is increasing demand for attractive and interactive content. Meeting the appetite for projects that do more and reach further than ever before places heavy demands on a project’s workflow. In this series, we demonstrate a modern workflow that uses simple building blocks to turn high-quality analytics into memos, papers, presentations, and even web pages – and it’s easy to do. Even participants that have never written a line of code will create and host a webpage in the first session. 

Constructed from easily accessed free services, this example workflow is designed from the ground-up to support teamwork, transparency, replicability, and a broad range of deliverables. We’ll show you how to recycle the same basic techniques to co-create products that are both tailored to the target audience and replicable by the world at-large. 

]

.pull-right[

### What You Will Learn

* .orange[**Personal Background**]: Born and raised in San Antonio, Texas. Live in Austin with my wife and three kids. 
* .orange[**Education Backgrounds**]: English Studies, Special Education, and Public Policy
* .orange[**Professional Backgrounds**]: Public School Teacher, School District Administrator, and Data Scientist. 
]

---



